MRP Case Study

### 2020-01-31 Code/mrp/Case Study .Rmd
Stan code added but not running. Working on fixes.

@@

>>>>

  coef_male <- c(0,-0.3)
  coef_eth <- c(0, 0.6, 0.9)
  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
  coef_income <- c(0,-0.2, 0.6)
  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
  true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
  for (j in 1:prod(J)) {
    true_popn$satisfaction[j] <- plogis(
      coef_male[poststrat[j, 1] + 1] +
        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
      )
  }
```

@@

```{r}
sim_values <- list(
  N = 6300,                                       # Number of observations.
  K = 2,                                         # Number of groups.
  I = 65,                                         # Number of observation-level covariates.

  male = sample(2, 6300, replace = TRUE),            # Vector of group assignments.
  eth = sample(3, 6300, replace = TRUE),       # Vector of brands covariates.
  age = sample(7, 6300, replace = TRUE),        # Vector of price covariates.
  income = sample(3, 6300, replace = TRUE),
  state = sample(50, 6300, replace = TRUE),

  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
  tau_min = 0,                                   # Minimum for the hyperprior on tau.
  tau_max = .1,                                   # Maximum for the hyperprior on tau.
  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
  sigma_max = .1                                  # Maximum for the hyperprior on tau.
)
# Generate data.
sim_data <- stan(
  file = here::here("Code/mrp/generate_data.stan"),
  data = sim_values,
  iter = 10,
  chains = 1,
  seed = 42,
  algorithm = "Fixed_param"
)
```

```{r}
# Extract the simulated data.
prior_pc <- tibble(
  cat_pref = as.vector(extract(sim_data)$cat_pref)
)
# Plot the prior predictive distribution.
prior_pc %>% 
  ggplot(aes(x = cat_pref)) +
  geom_density()
```

```{r}
# # Specify data.
# data <- list(
#   N = nrow(true_popn),                     # Number of observations.
#   K = 2,                    # Number of groups.
#   I = 65,                                # Number of observation-level covariates.
#   
#   cat_pref = true_popn$cat_pref,               # Vector of observations.
#   male = as.numeric(as.factor(true_popn$male)),            # Vector of group assignments.
#   eth = true_popn$eth,       # Vector of brands covariates.
#   age = true_popn$age,        # Vector of price covariates.
#   income = true_popn$income,
#   state = true_popn$state,
#   
#   gamma_mean = 0.5,                                # Mean for the hyperprior on gamma.
#   gamma_var = .2,                                 # Variance for the hyperprior on gamma.
#   tau_min = 0,                                   # Minimum for the hyperprior on tau.
#   tau_max = 1,                                   # Maximum for the hyperprior on tau.
#   sigma_min = 0,                                 # Minimum for the hyperprior on tau.
#   sigma_max = 1                                 # Maximum for the hyperprior on tau.
# )
# # Calibrate the model.
# model03 <- stan(
#   file = here::here("Code/mrp/hierarchical_model.stan"),
#   data = data,
#   control = list(adapt_delta = 0.99),
#   seed = 42
# )
```

```{r}
# Posterior predictive check.
# post_pc03 <- tibble(
#   # Extract the posterior predicted values.
#   intent = as.vector(extract(model03)$cat_pref_pc)
# )
# # Plot the posterior predictive distribution.
# ggplot(post_pc03, aes(x = intent)) +
#   geom_histogram() +
#   xlim(1, 10) 
# ggplot(purchase_intent, aes(x = intent)) +
#   geom_histogram() +
#   xlim(1, 10) 
```

```{r}
# model03 %>%
#   gather_draws(alpha[n, i]) %>%
#   unite(.variable, .variable, n, i) %>%
#   ggplot(aes(x = .value, y = .variable)) +
#   geom_halfeyeh(.width = .95) +
#   facet_wrap(
#     ~ .variable,
#     nrow = data$K,
#     ncol = (data$I - 1),
#     scales = "free"
#   )
```

```{r}
# Plot the betas.
# model03 %>%
#   gather_draws(beta[i]) %>%
#   unite(.variable, .variable, i) %>%
#   ggplot(aes(x = .value, y = .variable)) +
#   geom_halfeyeh(.width = .95) +
#   facet_wrap(
#     ~ .variable,
#     nrow = data$K,
#     ncol = 1,
#     scales = "free"
#   )
```
